---
output:
  md_document:
    variant: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# reproducer

The R package **reproducer** is aimed to support reproducible research in software engineering. See the package [homepage](https://cran.r-project.org/package=reproducer) for details and examples.

## Installation

One may install the stable version from
[CRAN](https://cran.r-project.org/package=reproducer):

```r
install.packages('reproducer', dependencies = TRUE)
```

You can use **devtools** to install the development version from my web site:

```r
install.packages("devtools", dependencies = T, repos = "https://cran.r-project.org/")
library(devtools)
devtools::install_url("https://madeyski.e-informatyka.pl/download/R/reproducer_0.5.3.tar.gz")
library(reproducer)
```

## Motivation
The motivation is to support using robust statistical methods and reproducible research in software engineering via sharing data sets and code behind the published or just submitted papers.


## Citation
If you use **reproducer**, please cite it:

```{r, echo = FALSE}
citation("reproducer")
```

## Status
[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/reproducer)](https://cran.r-project.org/package=reproducer)
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/reproducer)](https://cran.r-project.org/package=reproducer)
[![Downloads/month](https://cranlogs.r-pkg.org/badges/reproducer)](https://cran.r-project.org/package=reproducer)

